Suplementary Material 3: Run Simulations on the Last Birth Omited Data

### 2023-04-12 S3_run_simulations_EE_not_last.Rmd
simulations finished

```{r}
## Identify number of CPU cores available for parallel computing,
## note: using a large number may lead RAM to max out, so you may have to adjust
## that according to your infrastructure:
nb_cores <- 40

@@

```{r draw figure}
## Combine simulated slopes:

all_slopes <- combine_simulated_slopes(path_slopes = slopeDir)

## Figure 5:

fig5 <- draw_fig_5(all_slopes, width = 1)
fig5Fname <- paste0("./exports/fig5_", expName, ".")
ggplot2::ggsave(filename = paste0(fig5Fname, "pdf"), fig5,
                width = 88, height = 70, units = "mm")
fig5
```

@@

```{r timing}
## computing time (for gof analysis):

computing_time_analysis(all_slopes)

>>>>

```{r}
## Identify number of CPU cores available for parallel computing,
## note: using a large number may lead RAM to max out, so you may have to adjust
## that according to your infrastructure:
nb_cores <- 50

@@

```{r load slopes, include=FALSE}
## Combine simulated slopes:

all_slopes <- combine_simulated_slopes(path_slopes = slopeDir)
```

```{r}
#change the p-val expected direction
source("./R/twinR_goodness_of_fit.R")

# unchanged from the original but needed to have positive slopes yellow. 
source("./R/twinR_fig_5.R")
```

```{r draw figure}
## Figure 5 with colours inverted as we look for positive slopes:
fig5 <- draw_fig_5(all_slopes, width = 1)
fig5Fname <- paste0("./exports/fig5_", expName, ".")
ggplot2::ggsave(filename = paste0(fig5Fname, "pdf"), fig5,
                width = 88, height = 70, units = "mm")
fig5
```

@@

```{r timing, results='asis'}
## computing time (for gof analysis):
timeHours <- computing_time_analysis(all_slopes)
cat("Total CPU time to run simulations was ",
    unlist(round(timeHours / 24, 2)), "days. ",
    "On a high RAM desktop computer with 8 cores it would hence take around",
    unlist(round(timeHours / 24 / 8, 0)), "days to run. However, on a standard ",
    "desktop computer with 24 GB RAM only 1 core could be used.")
